---
title: My Awesome Report
author: Emmet Brickowski
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
```

# Level 1 header
## Level 2 header
### Level 3 header
#### You get the idea...

## Introduction

This report uses the **tidyverse** package along with the *SAFI*
dataset, which has columns that include:

- village
  + name of village
- interview_date
- no_membrs
- years_liv

These are my favourite variables ranked:

1. no_membrs
2. years_liv
3. interview_date

## Materials and methods

We used the *SAFI* dataset, which we downloaded from the source.

```
download.file("https://ndownloader.figshare.com/files/11492171", "data/SAFI_clean.csv", mode = "wb")
```

## Results

Table!

```{r interviews-table}
interviews %>%
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable()
```

### Data Viz

Here we will create some plots.

```{r}
interviews_plotting %>% 
  ggplot()
```

