---
title: My Awesome Report
author: Emmet Brickowski
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.path = "fig-")
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))
```

# Level 1 header
## Level 2 header
### Level 3 header
#### You get the idea...

## Introduction

This report uses the **tidyverse** package along with the *SAFI*
dataset, which has columns that include:

- village
  + name of village
- interview_date
- no_membrs
- years_liv

These are my favourite variables ranked:

1. no_membrs
2. years_liv
3. interview_date

## Materials and methods

We used the *SAFI* dataset, which we downloaded from the source.

```
download.file("https://ndownloader.figshare.com/files/11492171", "data/SAFI_clean.csv", mode = "wb")
```

## Results

Table!

```{r interviews-table}
interviews %>%
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable()
```

### Data Viz

Here we will create some plots.

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_point(alpha = 0.3)
```

Okay, scatter plot isn't the best for this...

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items)) +
    geom_jitter(
      alpha = 0.3,
      width = 0.2,
      height = 0.2,
      colour = "blue"
    )
```

```{r}
interviews_plotting %>% 
  ggplot(aes(x = no_membrs, y = number_items, col = village)) +
    geom_jitter(
      alpha = 0.3,
      width = 0.2,
      height = 0.2
    )
```


```{r}
interviews_plotting %>% 
  ggplot(aes(x = respondent_wall_type, y = rooms)) +
    geom_boxplot(alpha = 0) +
    geom_jitter(
      alpha = 0.3,
      height = 0.2,
      width = 0.2,
      colour = "tomato"
    )
```

#### Barplots

```{r barplot-1}
interviews_plotting %>% 
  ggplot(aes(x = respondent_wall_type)) +
  geom_bar(aes(fill = village), position = "dodge")
```

```{r}
percent_wall_type <- interviews_plotting %>% 
  filter(respondent_wall_type != "cement") %>% 
  count(village, respondent_wall_type) %>% 
  group_by(village) %>% 
  mutate(percent = (n / sum(n)) * 100) %>% 
  ungroup()
```

```{r percent-bar}
percent_wall_type %>% 
  ggplot(aes(
    x = village, 
    y = percent, 
    fill = respondent_wall_type)
  ) +
  geom_col(position = "dodge") +
  labs(
    title = "Plot title",
    fill = "Legend",
    x = "Village",
    y = "Percent"
  ) +
  scale_fill_viridis_d() +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 50, angle = 30)
  )
```


